```{r setup, include=FALSE, warning=FALSE, message=FALSE, comment=FALSE, error=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(magrittr)
library(overtime)
library(DT)
```

## Getting Started

-----

The intent of overtime is to help machine learning developers generate lots of summary statistics extremely quickly. While there are many default summary statistics initially processed, including more will be available in future releases. The default summary statistics are:

1. `sum`
2. `mean`
3. `median`
4. `sd`
5. `max`
6. `min`
7. `sd / mean` (coefficient of variation)
8. OO2
9. OO3
10. Largest positive sequence
11. Largest negative sequence
12. Largest zero sequence
13. Largest increasing sequence
14. Largest decreasing sequence
15. Largest increasing positive sequence
16. Largest decreasing positive sequence
17. Largest increasing negative sequence
18. Largest decreasing negative sequence

The actual content of the package is smaller than most, but its scope of usability is a wide net. Below is a simple example:  

```{r, echo=TRUE, warning=FALSE, message=FALSE, comment=FALSE, error=FALSE}
data <- readRDS('../data/rawData.rds') %>%
  filter(Date >= "2015-07-27" & Date <= "2015-07-29", AccountNumber < "D")

nestedData <- data %>%
  overtime_by("day") %>%
  overtime_get()

unnestedData <- nestedData %>%
  overtime_unnest()
```

BOOM! It's that simple.

### What it looks like

-----

#### Nested Data

```{r, echo=FALSE, warning=FALSE, message=FALSE, comment=FALSE, error=FALSE}
datatable(nestedData)
```

#### Unnested Data

```{r, echo=FALSE, warning=FALSE, message=FALSE, comment=FALSE, error=FALSE}
datatable(unnestedData)
```

-----

## Compatible data format
Currently, only a specific data format works with overtime. Here is an example data format:

| AccountNumber | Date       | Count |
| ------------- | ---------- | ----- |
| A             | 2014-11-01 | 1     |
| A             | 2014-11-02 | 4     |
| B             | 2014-11-01 | 0     |
| B             | 2014-11-01 | 12    |
| C             | 2014-11-02 | 8     |
| C             | 2014-11-01 | 47    |

There must be:

* Grouped variable column
* Continious dates column
    + All group variables must have equal number of dates
    + There can be no date jumps (eg. 2014-11-01 | 2014-11-03)
* Numeric counts column
    + Each cell must be a positive integer (eg. no _NA_ or -1)

## Reference
An [article](https://blog.appliedai.com/synthetic-data/#why) that talks to the benefit of data generated by `overtime`.

## Notes
_This package is in development. Functionality and documentation is being improved and polished_.